Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-12 TACAS2018/paper.tex
Some refinement of the abstract

\begin{abstract} 
%
We present a sound and automated approach to synthesize safe, digital
observer-based controllers for physical plants represented as linear,
time-invariant models.  Models are given as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors caused by
the digitization effects of the controller.  We use multi-staged
counterexample-guided inductive synthesis (CEGIS) with four phases: 1)~We
create a modular abstraction of the model and feed it to a two stage synthesiser
to reduce computational cost.  2)~We use the coarsest level of
abstraction to synthesise an approximate observer-based controller using
a Bounded Model Checker(BMC), and then  3)~We feed the imprecise result to
a second synthesiser based on eigendecomposition which uses a more precise
abstraction to refine the result.
The BMC is computationally more expensive, but able to reason
about more complex models, whereas the eigensolver is fast but requires a
reference candidate solution close to the desired result to guide the synthesis.
The intuition is that because our solutions form sets of connected spaces, 
the desired solution lies in the vicinity of a [possibly] unsuitable candidate
found by the first synthesiser.  4)~The refined candidate solution is still
unsound.  Safety and other design properties are then verified using continuous
and discrete-time reachability analysis tools.  If either verification
fails, a counterexample is provided to the modelling phase, which will refine
the abstraction based on the type of counter-example and feed it back to
the synthesisers.  The process iterates until a safe controller is obtained.
We demonstrate the practical value of this approach by automatically
synthesizing safe observer-based controllers for physical plant models from
the digital control literature.
%
\end{abstract}

@@

Using state of the art verifiers, we evaluate these models against
automatically synthesised controllers using CEGIS-based synsthesis that
incorporate the above mentioned artifacts in different models of
Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
that exploits different aspects of the problem at each stage.

@@

%The synthesiser uses a discrete time model that relates to the sampling
%time.  It begins with a very simple abstraction of the real system which
%only considers the static properties of the model.  It~also uses a very low
%precision bit vector representation of the real dynamics in order to
%minimise synthesis time.  
A candidate solution is then passed to a set of verifiers which will
evaluate the synthesised controller over an even more precise
abstraction of the concrete domain in both discrete and continuous
space/time.  This stage uses abstraction refinement when needed to ensure
that rejected candidates are not being discarded due to the
over-approximation.  The nature of the counterexamples varies depending on
the following conditions:
%
\begin{enumerate}
%
\item Initially, we look for possible errors caused by the restricted domain
of the synthesisers (e.g., overflows and rounding).  These will typically 
manifest in the static properties of the system. If an error is found, the
modeller is signalled to increase the precision of the synthesisers.
%
\item Next we explore the nature of the discrete-time progression to mark
a counterexample that relates to the progression of the system. If such a
counterexample exists, we indicate its initial conditions and time horizon,
thus instructing the synthesiser to refine its abstraction with respect to the
set of initial states and number of iterations. 
%
\item Continuous time analysis indicates the need for decreasing the
sampling time due to continuous excursions outside the safety region in
between samples.  This changes the problem statement of the synthesiser to a
new discrete-time model.
%
\item A final condition arises when a candidate solution cannot be found,
thus requiring higher precision of the abstraction numerical representation. 
We initially consider the plant representation to be too conservative and
may eventually increase the controller FWL specification when no controller
can be found for a given precision.
%
\end{enumerate}

>>>>

\begin{abstract} 
%
We present a sound and automated approach to synthesizing safe,
digital observer-based controllers for physical plants represented as
linear, time-invariant models.  Models are given as dynamical
equations with inputs, evolving over a continuous state space and
accounting for errors caused by the digitization effects of the
controller.  We use a two-stage counterexample-guided inductive
synthesis (CEGIS) driven by abstraction refinement: (1) The first,
coarse, synthesis stage uses a low resolution discretized model of the
original one and, initially, only looks at static properties of the
system.  (2) The second synthesis stage uses eigendecomposition to
refine the imprecise result computed by the first stage.  Whenever the
second stage is unable to find a candidate solution, it triggers an
abstraction refinement phase, resulting in a finer abstraction being
fed back to the first stage.  This design resulted in a significant
speed-up compared to a traditional single stage one.  We demonstrate
the practical value of this approach by automatically synthesizing
safe observer-based controllers for physical plant models from the
digital control literature.
%
\end{abstract}

@@

%\todo{reword paragraph?}
Using state of the art verifiers, we evaluate these models against
automatically synthesised controllers using CEGIS-based synsthesis that
incorporate the above mentioned artifacts in different models of
Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
that exploits different aspects of the problem at each stage.

@@

%The synthesiser uses a discrete time model that relates to the sampling
%time.  It begins with a very simple abstraction of the real system which
%only considers the static properties of the model.  It~also uses a very low
%precision bit vector representation of the real dynamics in order to
%minimise synthesis time.  
A candidate solution is then passed to a set of verifiers which will
evaluate the synthesised controller over an even more precise
abstraction of the concrete domain in both discrete and continuous
space/time.  This stage uses abstraction refinement when needed to ensure
that rejected candidates are not being discarded due to the
over-approximation.

\todo{remove until end of enumerate}
The nature of the counterexamples varies depending on
the following conditions:
%
\begin{enumerate}
%
\item Initially, we look for possible errors caused by the restricted domain
of the synthesisers (e.g., overflows and rounding).  These will typically 
manifest in the static properties of the system. If an error is found, the
modeller is signalled to increase the precision of the synthesisers.
%
\item Next we explore the nature of the discrete-time progression to mark
a counterexample that relates to the progression of the system. If such a
counterexample exists, we indicate its initial conditions and time horizon,
thus instructing the synthesiser to refine its abstraction with respect to the
set of initial states and number of iterations. 
%
\item Continuous time analysis indicates the need for decreasing the
sampling time due to continuous excursions outside the safety region in
between samples.  This changes the problem statement of the synthesiser to a
new discrete-time model.
%
\item A final condition arises when a candidate solution cannot be found,
thus requiring higher precision of the abstraction numerical representation. 
We initially consider the plant representation to be too conservative and
may eventually increase the controller FWL specification when no controller
can be found for a given precision.
%
\end{enumerate}
